Evaluation of classical correlation functions from 2/3D images on CPU and GPU architectures: introducing CorrelationFunctions.jl

### 2023-09-07 paper-correlations.tex
Fix a typo

\section{Applications and benchmarks}
After the verification of our computational approach based on analytical
solution, in this section we apply \code{CorrelationFUnctions.jl} to compute CFs
for a variety of real 2D (SEM) and 3D (XCT) images. We also report benchmarks on
execution time and compare the efficiency of GPU and CPU implementations.

>>>>

\section{Applications and benchmarks}
After the verification of our computational approach based on analytical
solution, in this section we apply \code{CorrelationFunctions.jl} to compute CFs
for a variety of real 2D (SEM) and 3D (XCT) images. We also report benchmarks on
execution time and compare the efficiency of GPU and CPU implementations.
